Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-25 doc/JFM2022/Final/main_jfm.tex

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by physicist Pierre-Gilles de Gennes as ``another animal in soft matter physics", the
Janus particle--often a spherical particle with a hydrophobic and a
hydrophilic hemisphere--exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering (\cite{deGennes1991}).
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
hydrodynamics interactions with both short- and intermediate-range 
particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig1.eps}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, and $A$ is the enclosed area.
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for the Janus suspension to incorporate the collective hydrodynamics of
a Janus suspension under various flows. The JP vesicles in our
simulations replicate well-known vesicle hydrodynamics
such as tank-treading and inter-leaflet slippage in a shear flow and
migration in Poiseuille flow from continuum models. Furthermore we use
the hybrid continuum model to investigate permeability and rupture of a
bilayer membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

@@

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively soft repulsive
force (compared to the short-range repulsion that diverges in the Lennard-Jones potential).

The paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime (Figure \ref{fig:figure0}a). In
\S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus
suspension to include the effects of a far-field flow via the mobility
problem formulation. In \S~\ref{results} we validate our model and
present simulation results for a single JP vesicle (Figure
\ref{fig:figure0}d) and for a pair of JP vesicles (Figure
\ref{fig:figure0}e) under various flowing conditions. Finally we provide
discussion and outlook for future directions in \S~\ref{conclusion}.

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
the no-slip boundary condition
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$.
Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
All derivatives are computed with spectrally-accurate
Fourier differentiation. Integrals that are smooth are computed with
the spectrally-accurate trapezoid rule, and nearly-singular integrals,
caused by close contact between two particles, are computed with a
high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
After discretizing and applying quadrature, the resulting linear system
is solved with matrix-free GMRES, and we guarantee that the number of
GMRES iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the
hydrophobic attraction potential (HAP) as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  \eta (\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
are
\begin{align}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
and has force $\FF_i$ while the rotlet is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, and
imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

We have validated our solver for~\eqref{eq:SKIE}--\eqref{eq:mobility2}
using a single elliptical particle suspended in a background shear flow
(see \S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion
are zero for a single particle (see \cite{Fu20} equation 2.13). The
angle of the ellipse's major axis coming from the integral equation
method agrees with the theoretical, Jeffery orbit time-course
(\cite{jef1922}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=11.5cm]{fig2.eps}
  \caption{\label{figure3} 
  JP vesicles undergo tank-treading in shear flow. 
  In panel (a),  the initial, 58-body vesicle is circular and the black arrows point in the direction of the
  hydrophobic side of the JP.
  In panel (b), the JP suspension rotates and deforms with the shear flow.
  The color map is for the solution $u$ of \eqref{eq:SL}. 
  The white curves are the streamlines of $\uu.$ 
   The shear rate is $\chi=0.0025$.}
\end{figure}

@@

We point out that the range of values for $\chi$ where we measured for
tank-treading correspond to shear rates $\dot \gamma = \mathcal{O}(10^6$
s$^{-1}$) which gives fluid velocities $\mathcal{O}($m s$^{-1}$$)$ in
the vicinity of the vesicle. While large, these orders of magnitude are identical to
ones used in prior MD studies (\cite{Brandner2019}) and are a
consequence of the fact that larger shear rates are required to produce
the viscous stresses needed to appreciably deform smaller vesicles.

>>>>

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and, at large shear rates, membrane rupture. 
  The simulation studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
  interactions between two, Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
  particle vesicle is similar to the behaviour of an inextensible, elastic vesicle membrane with permeability.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by physicist Pierre-Gilles de Gennes as ``another animal in soft matter physics", the
Janus particle--often a spherical particle with a hydrophobic and a
hydrophilic hemisphere--exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering (\cite{deGennes1991}).
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
hydrodynamics interactions with both short- and intermediate-range 
particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
a ``thin film of Janus grains" that can breathe due to the interstices between particles.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig1.eps}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution 
  $\eta$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve and $A$ is the enclosed area.
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for suspensions to incorporate the collective hydrodynamics of
a JP suspension under various flows. The JP vesicles in our
simulations replicate well-known vesicle hydrodynamics
such as tank-treading and inter-leaflet slippage in a shear flow and
migration in Poiseuille flow from continuum models. Furthermore we use
the hybrid continuum model to investigate permeability as well as rupture of a
bilayer membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

@@

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively soft repulsive
force compared to the short-range repulsion that diverges in the Lennard-Jones potential.

The paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime (Figure \ref{fig:figure0}a). In
\S~\ref{sec:IEM}, we extend the hybrid continuum model for a Janus
suspension to include the effects of a far-field flow via the mobility
problem formulation. In \S~\ref{results}, we validate our model and
present simulation results for a single JP vesicle (Figure
\ref{fig:figure0}d) and for a pair of JP vesicles (Figure
\ref{fig:figure0}e) under various flowing conditions. Finally we provide
discussion and outlook for future directions in \S~\ref{conclusion}.

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background velocity, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
the no-slip boundary condition
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair of particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \frac{M}{\rho_0} \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
     P'\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \frac{M}{\rho_0} \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
     P'\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
\end{align}
The repulsion profile $P(r/\rho_0)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = 1 - \sin(\pi r/2)$.
Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complicated domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
All derivatives are computed with spectrally-accurate
Fourier differentiation. Integrals that are smooth are computed with
the spectrally-accurate trapezoid rule, and nearly-singular integrals,
caused by close contact between two particles, are computed with a
high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
After discretizing and applying quadrature, the resulting linear system
is solved with matrix-free GMRES, and we guarantee that the number of
GMRES iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to the previous work (\cite{Fu20}), we represent the
hydrophobic attraction potential (HAP) as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  \eta (\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslets and rotlets centred at $\aa_i$
are
\begin{align}
\label{eq:stokeslet}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
    \label{eq:rotlet}
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet~\eqref{eq:stokeslet}  is torque-free
and has force $\FF_i$ while the rotlet~\eqref{eq:rotlet} is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, 
%and imposing that $\DD[\eeta]$ is force- and torque-free, 
%
the density function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= 0, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

We validated our solver for~\eqref{eq:SKIE}--\eqref{eq:mobility2}
using a single elliptical particle suspended in a background shear flow
(see \S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion
are zero for a single particle (see \cite{Fu20} equation 2.13). The
angle of the ellipse's major axis coming from the integral equation
method agreed with the theoretical, Jeffery orbit time-course
(\cite{jef1922}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=11.5cm]{fig2.eps}
  \caption{\label{figure3} 
  JP vesicles undergo tank-treading in shear flow. 
  In panel (a),  the initial, 58-body vesicle is circular and the black arrows point in the direction of the
  hydrophobic side of the JP.
  In panel (b), the JP suspension rotates and deforms with the shear flow.
  The color map is for the solution $\eta$ of \eqref{eq:SL}. 
  The white curves are the streamlines of $\uu.$ 
   The shear rate is $\chi=0.0025$.}
\end{figure}

@@

We point out that the range of values for $\chi$ where we measured for
tank-treading correspond to shear rates $\dot \gamma = \mathcal{O}(10^6$
s$^{-1}$) which gives fluid velocities $\mathcal{O}($m s$^{-1}$$)$ in
the vicinity of the vesicle. While large, these orders of magnitude are identical to
ones used in prior MD studies (\cite{Brandner2019}) and are a
consequence of the fact that large shear rates are required to produce
the viscous stresses needed to appreciably deform small vesicles.
